DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-02 paper/evaluation.tex
Add bus accesses to Figure 9

Figure~\ref{fig:} shows the normalized execution time and L2 miss-rate
of the DNN model running on the Core 0 as a function of the number of
co-scheduled memory intensive synthetic benchmarks. First, as we
increase the number of co-runners, the DNN model's execution times are
increased---by up to 11.6X---even though the DNN model is running on a
dedicated core (Core 0). On the other hand, the DNN model's L2
cache-miss rates do not increase as much.
In other words, the DNN model's execution increase is not fully
explained by increased contention in the L2 cache space.
Instead, the high memory bandwidth pressure from the co-scheduled
memory intensive benchmarks is likely the primary cause.

>>>>

Figure~\ref{fig:} shows the normalized execution time and L2 miss-rate
of the DNN model running on the Core 0 as a function of the number of
co-scheduled memory intensive synthetic benchmarks. First, as we
increase the number of co-runners, the DNN model's execution times are
increased---by up to 11.6X---even though the DNN model is running on a
dedicated core (Core 0). On the other hand, the DNN model's L2
cache-miss rates do not increase as much.
In other words, the DNN model's execution increase is not fully
explained by increased contention in the L2 cache space. Instead, the 
total number of bus accesses made while the model is running increases
dramatically, which explains why the DNN's performance decreased.
As such, the high memory bandwidth pressure from the co-scheduled
memory intensive benchmarks is likely the primary cause.
